High-order cognition is supported by information-rich but compressible brain activity patterns

### 2023-03-09 paper/main.tex
did some code reorganization, added network figure (fig 4) + updated caption

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/decode_pcs_network}

  \caption{\textbf{Network-specific decoding accuracy and compression.}
  \textbf{A. Decoding accuracy and number of components for network-specific
  inflection points.} We considered the seven networks identified by
  \cite{YeoEtal11}. We computed each network's inflection point, for each
  experimental condition, using the procedure described in
  Figure~\ref{fig:inflection}C. \textbf{B. Network-specific decoding
  accuracy.} Each of the seven networks are colored according to the decoding
  accuracy at the network's inflection point for the ``intact'' experimental
  condition (corresponding to the dark blue curve in Panel A). \textbf{C.
  Network-specific compression.} Each of the seven networks are colored
  according to the number of components at the network's inflection point for
  the intact experimental condition. Larger numbers of components reflect lower
  compressibility.}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.9\textwidth]{figs/network_results}

  \caption{\textbf{Network-specific decoding accuracy and compression.}
  \textbf{A. Network parcellation map.} The glass brain displays the location
  of each of seven networks identified by \cite{YeoEtal11}. \textbf{B. Node
  labels.} We assigned network labels to each of 700 Hierarchical Topographic
  Factor Analysis-derived nodes (see \textit{Hierarchical topographic factor
  analysis (HTFA)}). For each node, we evaluated its radial basis function
  (RBF) at the locations of every voxel in the parcellation map displayed in
  Panel A. We summed up these RBF weights separately for the voxels in each
  network. We defined each node's network label as its highest-weighted network
  across all voxels. \textbf{C. Per-network node counts.} The bar plot displays
  the total number of HTFA-derived nodes assigned to each network. \textbf{D.
  Informativeness versus compressibility by network and condition.} Each dot
  corresponds to a single cross validation run. The dots' coordinates denote
  the minimum proportion of components (relative to the number of nodes in the
  given network) required to achieve at least 5\% corrected decoding accuracy
  ($x$-coordinate; for the rest condition these proportions are estimated using
  the peak decoding accuracies) and peak (corrected) decoding accuracy
  ($y$-coordinate). We repeated the analysis separately for each network
  (color) and experimental condition (column). \textbf{E. Informativeness by
  network.} For each network, sorted (roughly) from lower-order networks on the
  left to higher-order networks on the right, the curves display the peak
  (corrected) decoding accuracy for each experimental condition (color).
  \textbf{F. Compressibility by network.} For each network, the curves display
  the proportion of components (relative to the total possible number of
  components displayed in Panel C) required to achieve at least 5\% decoding
  accuracy (or, for the rest condition, peak decoding accuracy, as described
  above). Error ribbons in Panels E and F denote 95\% bootstrap-estimated
  confidence intervals.}
